$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-02 paper/appendix.tex
Fix several slips

\begin{figure}[h]
  \begin{equation}
    \begin{split}
      &\field{IDX}          &:{} &\Set \\
      &\field{\exists IDX}  &:{} &\field{IDX} \\
      &\field{CARRIER}      &:{} &\field{IDX} \to \Set \\
      &\field{QUANTIFIERS}  &:{} &(i : \field{IDX}) \to \Quantifier_{\field{CARRIER}_i}
    \end{split}
  \end{equation}
  \caption{Indexed set of usage algebras.}
  \label{fig:indexed-multiplicities}
\end{figure}

>>>>

\begin{figure}[h]
  \begin{equation}
    \begin{split}
      &\field{IDX}          &:{} &\Set \\
      &\field{\exists IDX}  &:{} &\field{IDX} \\
      &\field{USAGE}        &:{} &\field{IDX} \to \Set \\
      &\field{QUANTIFIERS}  &:{} &(i : \field{IDX}) \to \Quantifier_{\field{USAGE}_i}
    \end{split}
  \end{equation}
  \caption{Indexed set of usage algebras.}
  \label{fig:indexed-multiplicities}
\end{figure}

### 2020-05-02 paper/paper.tex
Fix several slips

\begin{note}
  We will often work with pairs of input and output multiplicities.
  We use the notation $\Usage^2$ to stand for a $\Usage \times \Usage$ tuple of input and output multiplicities, respectively.
  We use $\op{x}{y}{z}$ to stand for a monoidal operation on pairs of multiplicities -- where the algebraic laws are lifted elementwise.
  Henceworth, we use $\lz$ to denote the pair $(0 \comma 0)$, $\li$ for the pair $(1 \comma 0)$, $\lo$ for $(0 \comma 1)$ and $\lio$ for $(1 \comma 1)$, borrowing from the linear \picalc{} notation \cite{KPT96,Sangio01}.
\end{note}

@@

@@

\begin{nidefinition}
  We use indexed sets of usage algebras to allow several usage algebras to coexist in our type system.
  An indexed set of usage algebras is a set of indices together with an interpretation of indices into types, and an interpretation of indices into usage algebras on that type.
  This indexed set must be non-empty.
  Refer to \autoref{fig:indexed-multiplicities} in \autoref{app:usage-algebra} for a formal definition.
\end{nidefinition}

>>>>

@@

\begin{nidefinition}
  We use indexed sets of usage algebras to allow several usage algebras to coexist in our type system.
  An indexed set of usage algebras is a set of indices $\Idx$ together with an interpretation $\Usage_{idx}$ of indices into types, and an interpretation of indices into usage algebras on that type.
  $\Idx$ must be non-empty.
  Refer to \autoref{fig:indexed-multiplicities} in \autoref{app:usage-algebra} for a formal definition.
\end{nidefinition}

\begin{note}
  We will often work with pairs of input and output multiplicities.
  We use the notation $\Usage_{idx}^2$ to stand for a $\Usage_{idx} \times \Usage_{idx}$ tuple of input and output multiplicities, respectively.
  We use $\opsquared{x}{y}{z}$ to stand for a monoidal operation on pairs of multiplicities -- where the algebraic laws are lifted elementwise.
  Henceworth, we use $\lz$ to denote the pair $(0 \comma 0)$, $\li$ for the pair $(1 \comma 0)$, $\lo$ for $(0 \comma 1)$ and $\lio$ for $(1 \comma 1)$, borrowing from the linear \picalc{} notation \cite{KPT96,Sangio01}.
\end{note}

@@
